---
title: "NBA Birthday Analysis"
author: "McCade Pearson"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

<style>
@import url('https://fonts.googleapis.com/css2?family=Barlow+Semi+Condensed:wght@300;400;600;700&display=swap');

body {
  background-color: #0D1117;
  color: #F0F3F5;
  font-family: 'Barlow Semi Condensed', sans-serif;
  font-size: 16px;
  line-height: 1.6;
  margin: 0;
  padding: 20px;
}

.main-container {
  max-width: 1000px;
  margin: 0 auto;
  background-color: #1C1F26;
  padding: 40px;
  border: 2px solid #3E92CC;
  border-radius: 8px;
}

h1, h2, h3, h4, h5, h6 {
  color: #C3DDFD;
  font-weight: 600;
  margin-top: 30px;
  margin-bottom: 15px;
}

h1 {
  font-size: 2.2em;
  text-align: center;
  border-bottom: 3px solid #3E92CC;
  padding-bottom: 10px;
}

h2 {
  font-size: 1.8em;
  color: #6FB1FC;
}

h3 {
  font-size: 1.4em;
  color: #326DA8;
}

pre {
  background-color: #0D1117;
  border: 1px solid #3E92CC;
  border-radius: 5px;
  padding: 15px;
  overflow-x: auto;
}

code {
  background-color: #1C1F26;
  color: #C3DDFD;
  padding: 2px 4px;
  border-radius: 3px;
  font-family: 'Courier New', monospace;
}

pre code {
  background-color: transparent;
  padding: 0;
}

a {
  color: #6FB1FC;
  text-decoration: none;
}

a:hover {
  color: #C3DDFD;
  text-decoration: underline;
}

blockquote {
  border-left: 4px solid #3E92CC;
  margin: 20px 0;
  padding-left: 20px;
  color: #C3DDFD;
  font-style: italic;
}

table {
  border-collapse: collapse;
  width: 100%;
  margin: 20px 0;
}

th, td {
  border: 1px solid #3E92CC;
  padding: 12px;
  text-align: left;
}

th {
  background-color: #326DA8;
  color: #F0F3F5;
  font-weight: 600;
}

tr:nth-child(even) {
  background-color: #1C1F26;
}

.author, .date {
  text-align: center;
  color: #6FB1FC;
  font-size: 1.1em;
}
</style>

```{r setup, include=FALSE}
library(tidyverse)
library(lubridate)
library(stringr)
library(showtext)
library(sysfonts)
library(gt)
library(scales)
library(gtExtras)
```

```{r Theme, warning = FALSE, message = FALSE, include = FALSE}
McCadeP8_theme_colors <- c(
  background = '#0D1117',   # dark slate gray (background)
  text       = '#F0F3F5',   # very light gray (text)
  panel      = '#1C1F26',   # near-black with blue hint (panel)
  border     = '#3E92CC',   # strong blue (border)
  strip_text = '#0D1117',   # matches background (strip text on light facet)
  lighter    = '#C3DDFD',   # baby blue
  light      = '#6FB1FC',   # sky blue
  medium     = '#326DA8',   # Jazz navy
  dark       = '#1D3557'    # deep indigo/navy
)

McCadeP8_palette <- c(
  '#C3DDFD', '#F94144', '#6A4C93', '#F9C74F', '#43AA8B',
  '#577590', '#F3722C', '#277DA1', '#264653'
)

## McCade Pearson
## theme_McCadeP8
## Date Created: June 10, 2025

# THEME COLOR PALETTE --------------------------------------

#' McCadeP8 Inspired Theme Color Palette
#'
#' @format character vector of hex code strings
#' @export
#' @concept McCadeP8
#'
McCadeP8_theme_colors <- c(
  background = '#0D1117',
  text       = '#F0F3F5',
  panel      = '#1C1F26',
  border     = '#3E92CC',
  strip_text = '#0D1117',
  lighter    = '#C3DDFD',
  light      = '#6FB1FC',
  medium     = '#326DA8',
  dark       = '#1D3557'
)

# DISCRETE COLOR PALETTE -----------------------------------

#' McCadeP8 Inspired Color Palette
#'
#' @format character vector of hex code strings
#' @export
#' @concept McCadeP8
#'
McCadeP8_palette <- c(
  '#C3DDFD', '#F94144', '#6A4C93', '#F9C74F', '#43AA8B',
  '#577590', '#F3722C', '#277DA1', '#264653'
)

# MAIN THEME ------------------------------------------------

#' McCadeP8 Inspired Theme
#'
#' @param McCadeP8_font should `theme_McCadeP8` use custom font? Default is `TRUE`.
#' @param ... additional parameters to pass to `ggplot2::theme()`
#'
#' @return a `ggplot2` `theme` object
#' @export
#' @concept McCadeP8
#'
theme_McCadeP8 <- function(McCadeP8_font = TRUE, ...) {

  # Load custom Google Font
  font_family <- ifelse(McCadeP8_font, "Barlow Semi Condensed", "sans")
  if (McCadeP8_font) {
  font_add_google(name = "Barlow Semi Condensed", family = "Barlow Semi Condensed")
  showtext_auto()
  }

  # Define the theme
  ggplot2::theme(
    plot.background = element_rect(fill = McCadeP8_theme_colors["background"], color = NA),
    panel.background = element_rect(fill = McCadeP8_theme_colors["panel"], color = NA),
    panel.border = element_rect(color = McCadeP8_theme_colors["border"], fill = NA, linewidth = 1.2),
    panel.grid.major = element_line(color = "#2D3748", size = 0.25),
    panel.grid.minor = element_blank(),
    
    text = element_text(color = McCadeP8_theme_colors["text"], family = font_family),
    title = element_text(size = 20, face = "bold", hjust = 0.5),
    axis.title = element_text(size = 17),
    axis.text = element_text(size = 13, color = McCadeP8_theme_colors["text"]),
    axis.ticks = element_line(color = McCadeP8_theme_colors["border"], linewidth = 1),
    
    legend.background = element_rect(fill = McCadeP8_theme_colors["panel"], color = NA),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 14, face = "bold"),
    
    strip.background = element_rect(fill = McCadeP8_theme_colors["lighter"], colour = McCadeP8_theme_colors["border"]),
    strip.text = element_text(colour = McCadeP8_theme_colors["strip_text"], size = 10)
  )
}

# COLOR SCALES ---------------------------------------------

#' McCadeP8 Inspired Color Scales
#'
#' @param ... Additional arguments to pass to `ggplot2::binned_scale` for `_b`,
#' `ggplot2::scale_[fill/color]_gradient` for `_c`, or `ggplot2::discrete_scale`
#' for `_d`
#'
#' @rdname scale_McCadeP8
#' @export
scale_color_McCadeP8_c <- function(...) {
  ggplot2::scale_color_gradient(..., low = McCadeP8_theme_colors["light"], high = McCadeP8_theme_colors["dark"])
}

#' @rdname scale_McCadeP8
#' @export
scale_fill_McCadeP8_c <- function(...) {
  ggplot2::scale_fill_gradient(..., low = McCadeP8_theme_colors["light"], high = McCadeP8_theme_colors["dark"])
}

#' @rdname scale_McCadeP8
#' @export
scale_color_McCadeP8_b <- function(...) {
  if (!requireNamespace('scales', quietly = TRUE)) {
    stop('This function requires the `scales` R package.')
  }
  ramp <- scales::colour_ramp(c(McCadeP8_theme_colors["light"], McCadeP8_theme_colors["dark"]))
  ggplot2::binned_scale('color', 'McCadeP8', palette = ramp, ...)
}

#' @rdname scale_McCadeP8
#' @export
scale_fill_McCadeP8_b <- function(...) {
  if (!requireNamespace('scales', quietly = TRUE)) {
    stop('This function requires the `scales` R package.')
  }
  ramp <- scales::colour_ramp(c(McCadeP8_theme_colors["light"], McCadeP8_theme_colors["dark"]))
  ggplot2::binned_scale('fill', 'McCadeP8', palette = ramp, ...)
}

#' @rdname scale_McCadeP8
#' @export
scale_color_McCadeP8_d <- function(...) {
  ggplot2::discrete_scale(aesthetics = 'color',
                          palette = rot_pal(McCadeP8_palette), ...)
}

#' @rdname scale_McCadeP8
#' @export
scale_fill_McCadeP8_d <- function(...) {
  ggplot2::discrete_scale(aesthetics = 'fill',
                          palette = rot_pal(McCadeP8_palette), ...)
}

# Aliases
#' @rdname scale_McCadeP8
#' @export
scale_colour_McCadeP8_d <- scale_color_McCadeP8_d
#' @rdname scale_McCadeP8
#' @export
scale_colour_McCadeP8_c <- scale_color_McCadeP8_c
#' @rdname scale_McCadeP8
#' @export
scale_colour_McCadeP8_b <- scale_color_McCadeP8_b
```

```{r}
#months <- 1:12
#days_in_month <- c(31, 28, 31, 30, 31, 30, 31, 31, 30, 31, 30, 31)
#
#Tables <- data.frame()
#
#for (month in months) {
#  for (day in 1:days_in_month[month]) {
#    filmURL <- read_html(paste("https://www.basketball-reference.com/friv/birthdays#.fcgi?month=", month, "&day=", day, sep = ""))
#    allTables <- filmURL %>%
#      html_table(fill = TRUE)
#    Results <- allTables[[1]]
#    Results <- Results %>%
#      row_to_names(row_number = 1) %>%
#      clean_names()
#    Results$month <- month
#    Results$day <- day
#    Results <- Results %>%
#      filter(player != "Player") %>%
#      filter(player != "")
#    Tables <- rbind(Results,Tables)
#    print(paste(month, day, Sys.time(), sep = "-"))
#    Sys.sleep(1.5)}}
Tables <- read.csv("AllPlayers.csv")
```


```{r}
Tables2 <- Tables %>%
  mutate(
    player = str_remove(player, "\\*$"),
    rk = as.numeric(rk),
    yrs = as.numeric(yrs),
    g = as.numeric(g),
    mp = as.numeric(mp),
    fg = as.numeric(fg),
    fga = as.numeric(fga),
    x3p = as.numeric(x3p),
    x3pa = as.numeric(x3pa),
    ft = as.numeric(ft),
    fta = as.numeric(fta),
    orb = as.numeric(orb),
    trb = as.numeric(trb),
    ast = as.numeric(ast),
    stl = as.numeric(stl),
    blk = as.numeric(blk),
    tov = as.numeric(tov),
    pf = as.numeric(pf),
    pts = as.numeric(pts),
    ws = as.numeric(ws),
    fg_percent = as.numeric(fg_percent),
    x3p_percent = as.numeric(x3p_percent),
    ft_percent = as.numeric(ft_percent),
    mp_2 = as.numeric(mp_2),
    pts_2 = as.numeric(pts_2),
    trb_2 = as.numeric(trb_2),
    ast_2 = as.numeric(ast_2),
    doy = yday(make_date(year = birth, month = month, day = day)))

Tables3 <- Tables2 %>%
  filter(g >= 100) %>%
  filter(born >= 1935) %>%
  group_by(doy) %>%
  mutate(RkPts = rank(-pts, ties.method = "random"),
         RkReb = rank(-trb, ties.method = "random"),
         RkAst = rank(-ast, ties.method = "random"),
         WSp48 = ws/mp*48,
         RkWS48 = rank(-WSp48, ties.method = "random")) %>%
  select(player, born, g, pts, trb, ast, WSp48, RkPts, RkReb, RkAst, RkWS48, doy, month, day) %>%
  ungroup()
```


```{r}
GetDatesPts <- Tables3 %>%
  filter(RkPts == 1) %>%
  rowwise() %>%
  mutate(Window = list(((doy - 2):(doy + 2) - 1) %% 365 + 1)) %>%
  unnest(Window) %>%
  select(Window, pts)
RkPts <- Tables3 %>%
  filter(RkPts == 1) %>%
  left_join(GetDatesPts, by = c('doy' = 'Window')) %>%
  group_by(doy) %>%
  mutate(pts.z = sum(pts.y)) %>%
  ungroup() %>%
  arrange(-pts.z) %>%
  select(doy, pts.z) %>%
  head(1)
Doy <- RkPts$doy[1]
Value <- RkPts$pts.z[1]
PtsResults <- Tables3 %>%
  filter(RkPts == 1) %>%
  filter(doy >= Doy-2 & doy <= Doy+2) %>%
  arrange(month,day) %>%
  mutate(date = paste0(month.abb[month], " ", day, ", ", born),
         Pic = c("https://www.basketball-reference.com/req/202106291/images/headshots/chambwi01.jpg","https://www.basketball-reference.com/req/202106291/images/headshots/catlete01.jpg","https://www.basketball-reference.com/req/202106291/images/headshots/bryanko01.jpg","https://www.basketball-reference.com/req/202106291/images/headshots/millere01.jpg","https://www.basketball-reference.com/req/202106291/images/headshots/horryro01.jpg")) %>%
  select(date, Pic, player, pts)


gt(PtsResults) %>%
  gt_theme_espn() %>%
  text_transform(locations = cells_body(columns = Pic),
      fn = function(x) {web_image(url = PtsResults$Pic, height = as.numeric(40))}) %>%
  cols_align(align = c('center')) %>%
  cols_label(date = "Birthday",
             player = "Player",
             pts = "Points",
             Pic = "") %>%
  tab_header(title = md("**The Best Five-Day Run of Basketball Birthdays**"),
             subtitle = md("104,576 Points")) %>%
  opt_align_table_header(align = c('center')) %>%
  tab_source_note(source_note = "@McCadeP8 | Data: basketball-reference") %>%
  fmt_number(columns = c(pts), use_seps = T, decimals = 0)

```

```{r}
GetDatesReb <- Tables3 %>%
  filter(RkReb == 1) %>%
  rowwise() %>%
  mutate(Window = list(((doy - 2):(doy + 2) - 1) %% 365 + 1)) %>%
  unnest(Window) %>%
  select(Window, trb)
RkReb <- Tables3 %>%
  filter(RkReb == 1) %>%
  left_join(GetDatesReb, by = c('doy' = 'Window')) %>%
  group_by(doy) %>%
  mutate(trb.z = sum(trb.y)) %>%
  ungroup() %>%
  arrange(-trb.z) %>%
  select(doy, trb.z) %>%
  head(1)
Doy <- RkReb$doy[1]
Value <- RkReb$trb.z[1]
RebResults <- Tables3 %>%
  filter(RkReb == 1) %>%
  filter(doy >= Doy-2 & doy <= Doy+2) %>%
  arrange(month,day) %>%
  select(player, born, trb, month, day)

GetDatesAst <- Tables3 %>%
  filter(RkAst == 1) %>%
  rowwise() %>%
  mutate(Window = list(((doy - 2):(doy + 2) - 1) %% 365 + 1)) %>%
  unnest(Window) %>%
  select(Window, ast)
RkAst <- Tables3 %>%
  filter(RkAst == 1) %>%
  left_join(GetDatesAst, by = c('doy' = 'Window')) %>%
  group_by(doy) %>%
  mutate(ast.z = sum(ast.y)) %>%
  ungroup() %>%
  arrange(-ast.z) %>%
  select(doy, ast.z) %>%
  head(1)
Doy <- RkAst$doy[1]
Value <- RkAst$ast.z[1]
AstResults <- Tables3 %>%
  filter(RkAst == 1) %>%
  filter(doy >= Doy-2 & doy <= Doy+2) %>%
  arrange(month,day) %>%
  left_join(RebResults, by = c('month', 'day')) %>%
  mutate(date = paste0(month.abb[month], " ", day),
         Pic.x = c("https://www.basketball-reference.com/req/202106291/images/headshots/shawbr01.jpg","https://www.basketball-reference.com/req/202106291/images/headshots/kiddja01.jpg","https://www.basketball-reference.com/req/202106291/images/headshots/fordtj01.jpg","https://www.basketball-reference.com/req/202106291/images/headshots/lowryky01.jpg","https://www.basketball-reference.com/req/202106291/images/headshots/stockjo01.jpg"),
         Pic.y = c("https://www.basketball-reference.com/req/202106291/images/headshots/cambyma01.jpg","https://www.basketball-reference.com/req/202106291/images/headshots/malonmo01.jpg","https://www.basketball-reference.com/req/202106291/images/headshots/boshch01.jpg","https://www.basketball-reference.com/req/202106291/images/headshots/davisda01.jpg","https://www.basketball-reference.com/req/202106291/images/headshots/embrywa01.jpg")) %>%
  select(date, born.x, Pic.x, player.x, ast, born.y, Pic.y, player.y, trb.y)

gt(AstResults) %>%
  gt_theme_espn() %>%
  text_transform(locations = cells_body(columns = Pic.x),
      fn = function(x) {web_image(url = AstResults$Pic.x, height = as.numeric(40))}) %>%
    text_transform(locations = cells_body(columns = Pic.y),
      fn = function(x) {web_image(url = AstResults$Pic.y, height = as.numeric(40))}) %>%
  cols_align(align = c('center')) %>%
  cols_label(date = "Birthday",
             born.x = "Year",
             born.y = "Year",
             player.x = "Player",
             player.y = "Player",
             trb.y = "Rebounds",
             ast = "Assists",
             Pic.x = "",
             Pic.y = "") %>%
  tab_header(title = md("**The Best Five-Day Run of Basketball Birthdays**"),
             subtitle = md("Remarkably, both lineups fall on March 22–26—yet share no players in common")) %>%
  opt_align_table_header(align = c('center')) %>%
  tab_source_note(source_note = "@McCadeP8 | Data: basketball-reference") %>%
  fmt_number(columns = c(ast,trb.y), use_seps = T, decimals = 0) %>%
  tab_spanner(label = "41,409 Assists", columns = c(born.x, player.x, Pic.x, ast)) %>%
  tab_spanner(label = "51,088 Rebounds", columns = c(born.y, player.y, Pic.y, trb.y))
```

```{r}
GetDatesWS <- Tables3 %>%
  filter(RkWS48 == 1) %>%
  rowwise() %>%
  mutate(Window = list(((doy - 2):(doy + 2) - 1) %% 365 + 1)) %>%
  unnest(Window) %>%
  select(Window, WSp48)
RkWS <- Tables3 %>%
  filter(RkWS48 == 1) %>%
  left_join(GetDatesWS, by = c('doy' = 'Window')) %>%
  group_by(doy) %>%
  mutate(WSp48.z = sum(WSp48.y)) %>%
  ungroup() %>%
  arrange(-WSp48.z) %>%
  select(doy, WSp48.z) %>%
  head(1)
Doy <- RkWS$doy[1]
Value <- RkWS$WSp48.z[1]
WSResults <- Tables3 %>%
  filter(RkWS48 == 1) %>%
  filter(doy >= Doy-2 & doy <= Doy+2) %>%
  arrange(month,day) %>%
  mutate(date = paste0(month.abb[month], " ", day, ", ", born),
         WSp48 = round(WSp48,4),
         Pic = c("https://www.basketball-reference.com/req/202106291/images/headshots/jordami01.jpg","https://www.basketball-reference.com/req/202106291/images/headshots/kirilan01.jpg","https://www.basketball-reference.com/req/202106291/images/headshots/jokicni01.jpg","https://www.basketball-reference.com/req/202106291/images/headshots/barklch01.jpg","https://www.basketball-reference.com/req/202106291/images/headshots/francst01.jpg")) %>%
  select(date, Pic, player, WSp48)

gt(WSResults) %>%
  gt_theme_espn() %>%
  text_transform(locations = cells_body(columns = Pic),
      fn = function(x) {web_image(url = WSResults$Pic, height = as.numeric(40))}) %>%
  cols_align(align = c('center')) %>%
  cols_label(date = "Birthday",
             player = "Player",
             WSp48 = "WS per 48min",
             Pic = "") %>%
  tab_header(title = md("**The Strongest Five-Day Birthday Lineup in Basketball**")) %>%
  opt_align_table_header(align = c('center')) %>%
  tab_source_note(source_note = "@McCadeP8 | Data: basketball-reference")
```

```{r}
Total <- Tables2 %>%
  group_by(doy) %>%
  summarize(TotalG = sum(g, na.rm = TRUE))
Total2 <- Total %>%
  rowwise() %>%
  mutate(Window = list(((doy - 15):(doy + 15) - 1) %% 365 + 1)) %>%
  unnest(Window) %>%
  group_by(Window) %>%
  summarise(AvgG = mean(TotalG, na.rm = TRUE), .groups = "drop") %>%
  left_join(Total, by = c("Window" = "doy"))

ggplot(Total2) +
  geom_vline(xintercept = c(1, 32, 60, 91, 121, 152, 182, 213, 244, 274, 305, 335, 365), color = "#1D3557", linewidth = 0.5) +
  geom_point(aes(x = Window, y = TotalG), color = "#C3DDFD", alpha = 0.6) +
  geom_segment(aes(x = Window, xend = Window, y = AvgG, yend = TotalG), color = "#C3DDFD", alpha = 0.6) +
  geom_line(aes(x = Window, y = AvgG), color = "#326DA8", size = 2) +
  geom_segment(aes(x = 90, y = 11379, xend = 58, yend = 11379), arrow = arrow(length = unit(0.5, "cm"), type = "closed"), color = "#C3DDFD", size = 1) +
  geom_segment(aes(x = 330, y = 350, xend = 358, yend = 313), arrow = arrow(length = unit(0.5, "cm"), type = "closed"), color = "#C3DDFD", size = 1) +
  geom_segment(aes(x = 150, y = 8750, xend = 73, yend = 4900), arrow = arrow(length = unit(0.5, "cm"), type = "closed"), color = "#326DA8", size = 1) +
  geom_segment(aes(x = 249, y = 8750, xend = 249, yend = 4800), arrow = arrow(length = unit(0.5, "cm"), type = "closed"), color = "#326DA8", size = 1) +
  geom_label(aes(x = 75, y = 11379, label = "11,379 games played — Dr. J & Chet Walker (HoF), Rondo, Van Arsdale twins"), hjust = 0, size = 6.3, fill = "#C3DDFD") +
  geom_label(aes(x = 240, y = 8750, label = "Peak driven by kids born early in the calendar or school year, who had early physical advantages"), size = 6.2, fill = "#326DA8", color = "white") +
  geom_label(aes(x = 345, y = 350, label = "Only one player born this day since 1955: Briante Weber (45 games)"), hjust = 1, size = 6.2, fill = "#C3DDFD") +
  scale_x_continuous(limits = c(0, 366), breaks = c(16, 46, 75.5, 106, 136.5, 167, 197.5, 228.5, 259, 289.5, 320, 350), labels = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec")) +
  scale_y_continuous(limits = c(0, 12500), breaks = c(0, 2500, 5000, 7500, 10000, 12500), expand = c(0, 0), labels = comma) +
  labs(x = "",
       y = "Career Games Played",
       title = "Most Career Games Played by Birthday",
       caption = "@McCadeP8 | Data: basketball-reference") +
  theme_McCadeP8() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), plot.title = element_text(face = "bold", size = 24, hjust = 0.5))
```

