---
title: "NCFL Rosters"
author: "McCade Pearson"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

<style>
@import url('https://fonts.googleapis.com/css2?family=Barlow+Semi+Condensed:wght@300;400;600;700&display=swap');

body {
  background-color: #0D1117;
  color: #F0F3F5;
  font-family: 'Barlow Semi Condensed', sans-serif;
  font-size: 16px;
  line-height: 1.6;
  margin: 0;
  padding: 20px;
}

.main-container {
  width: 100%;
  max-width: none;   /* removes the 1000px cap */
  margin: 0;         /* removes centering margin */
  background-color: #1C1F26;
  padding: 40px;
  border: 2px solid #3E92CC;
  border-radius: 8px;
}

h1, h2, h3, h4, h5, h6 {
  color: #C3DDFD;
  font-weight: 600;
  margin-top: 30px;
  margin-bottom: 15px;
}

h1 {
  font-size: 2.2em;
  text-align: center;
  border-bottom: 3px solid #3E92CC;
  padding-bottom: 10px;
}

h2 {
  font-size: 1.8em;
  color: #6FB1FC;
}

h3 {
  font-size: 1.4em;
  color: #326DA8;
}

pre {
  background-color: #0D1117;
  border: 1px solid #3E92CC;
  border-radius: 5px;
  padding: 15px;
  overflow-x: auto;
}

code {
  background-color: #1C1F26;
  color: #C3DDFD;
  padding: 2px 4px;
  border-radius: 3px;
  font-family: 'Courier New', monospace;
}

pre code {
  background-color: transparent;
  padding: 0;
}

a {
  color: #6FB1FC;
  text-decoration: none;
}

a:hover {
  color: #C3DDFD;
  text-decoration: underline;
}

blockquote {
  border-left: 4px solid #3E92CC;
  margin: 20px 0;
  padding-left: 20px;
  color: #C3DDFD;
  font-style: italic;
}

table {
  border-collapse: collapse;
  width: 100%;
  margin: 20px 0;
}

th, td {
  border: 1px solid #3E92CC;
  padding: 12px;
  text-align: left;
}

th {
  background-color: #326DA8;
  color: #F0F3F5;
  font-weight: 600;
}

tr:nth-child(even) {
  background-color: #1C1F26;
}

.author, .date {
  text-align: center;
  color: #6FB1FC;
  font-size: 1.1em;
}
</style>



```{r setup, include=FALSE}
library(tidyverse)
library(httr)
library(jsonlite)
library(googlesheets4)
library(nflreadr)
library(gt)
library(htmltools)
library(gtExtras)

GetPlayers <- function() {
  # Bring in the player information
  player_response <- httr::GET("https://api.sleeper.app/v1/players/nfl",
                               config(ssl_verifypeer = 0))
  
  if (httr::status_code(player_response) == 200) {
    message("Player API call success")
    player_content <- httr::content(player_response, "text")
    player_parsed <- jsonlite::fromJSON(player_content)
    
    # Initialize an empty dataframe with specified columns
    player_ids <- names(player_parsed)
    player_df <- tibble::tibble(
      player_id = NA_character_,
      player_name = NA_character_,
      player_position = NA_character_,
      injury_status = NA_character_
    ) %>% tidyr::drop_na()
    
    # Loop through player IDs and extract relevant data
    for (i in seq_along(player_ids)) {
      player_of_interest <- player_ids[i]
      specific_player_data <- player_parsed[[player_of_interest]]
      
      new_row <- tibble::tibble(
        player_id = player_of_interest,
        player_name = specific_player_data[['full_name']],
        player_position = specific_player_data[['position']],
        injury_status = specific_player_data[['injury_status']]
      )
      
      player_df <- dplyr::bind_rows(player_df, new_row)
    }
    
    return(player_df)
  } else {
    stop(paste0("API call failed with status code ", httr::status_code(player_response)))
  }
}
sheet_key <- "1dE2dwV8DEtmg22YHic_V_7hndXLy_faL0MKB7FOaJzA"
Designations <- range_read(sheet_key, sheet = "Player_List")
2
SnapCounts <- nflreadr::load_snap_counts() %>%
  filter(offense_snaps >= 1) %>%
  filter(week <= 14) %>%
  group_by(player, pfr_player_id) %>%
  summarize(GP = n()) %>%
  select(-pfr_player_id)

Players <- GetPlayers()
Rosters <- GET("https://api.sleeper.app/v1/league/1266532194239664128/rosters", config(ssl_verifypeer = 0))
Rosters <- content(Rosters, "text")
Rosters <- fromJSON(Rosters)

TaxiRosters <- Rosters %>%
  unnest(taxi) %>%
  left_join(Players, c('taxi' = 'player_id')) %>%
  select(player_name) %>%
  pull()


FinalRosters <- Rosters %>%
  unnest(players) %>%
  left_join(Players, c('players' = 'player_id')) %>%
  filter(player_position %in% c('QB','RB','WR','TE')) %>%
  select(roster_id, player_name, player_position) %>%
  left_join(Designations, by = c('player_name' = 'Player')) %>%
  left_join(SnapCounts, by = c('player_name' = 'player')) %>%
  mutate(
    GP = ifelse(is.na(GP), 0, GP),
    player_position = factor(player_position, levels = c("QB", "RB", "WR", "TE")),
    Classification = factor(Classification, levels = c("Senior", "Junior", "Sophomore", "Freshman")),
    Redshirted = ifelse(Redshirted == "Yes", "shirt", "far fa-square"),
    GP = if_else(GP <= 4 & Redshirted == "far fa-square", "kit-medical", "far fa-square"),
    Taxi = if_else(player_name %in% TaxiRosters, 'taxi', "far fa-square"),
    roster_id = case_when(
      roster_id == 1 ~ "tksimpson14",
      roster_id == 2 ~ "Sweezzy",
      roster_id == 3 ~ "sterlingcole",
      roster_id == 4 ~ "perc3val",
      roster_id == 5 ~ "ThongBonestorm",
      roster_id == 6 ~ "McCadeP8",
      roster_id == 7 ~ "TobesEA",
      roster_id == 8 ~ "DickLongshaft",
      TRUE ~ NA_character_
    ))

GetRosterGT <- function(Team) {

FinalRosters %>%
  filter(roster_id == Team) %>%
  select(player_position, player_name, Classification, Redshirted, Taxi, GP) %>%
  arrange(Classification, player_position, desc(Redshirted)) %>%
  group_by(Classification) %>%
  gt() %>%
  cols_align(columns = everything(), align = 'center') %>%
  cols_align(columns = player_name, align = 'left') %>%
  cols_label(player_position = "POS",
             player_name = "Player",
             Redshirted = "RS") %>%
  gt_theme_538() %>%
  fmt_icon(Redshirted) %>%
  fmt_icon(GP) %>%
  fmt_icon(Taxi) %>%
  tab_header(title = md(Team)) %>%
  tab_style(style = cell_fill(color = "#c05e85"), locations = cells_body(rows = player_position == "QB")) %>%
  tab_style(style = cell_fill(color = "#46a2ca"), locations = cells_body(rows = player_position == "WR")) %>%
  tab_style(style = cell_fill(color = "#73c3a6"), locations = cells_body(rows = player_position == "TE")) %>%
  tab_style(style = cell_fill(color = "#cc8c4a"), locations = cells_body(rows = player_position == "RB"))}
GetRosterPosition <- function(Team) {
  
  FinalRosters %>%
    filter(player_position == Team) %>%
    mutate(roster_id = substr(roster_id,1,3)) %>%
    select(player_position,roster_id, player_name, Classification, Redshirted, Taxi, GP) %>%
    arrange(Classification, roster_id, desc(Redshirted)) %>%
    group_by(Classification) %>%
    gt() %>%
    cols_align(columns = everything(), align = 'center') %>%
    cols_align(columns = player_name, align = 'left') %>%
    cols_label(roster_id = "Team",
               player_name = "Player",
               Redshirted = "RS") %>%
    gt_theme_538() %>%
    fmt_icon(Redshirted) %>%
    fmt_icon(GP) %>%
    fmt_icon(Taxi) %>%
    cols_hide(player_position) %>%
    tab_header(title = md(Team)) %>%
    tab_style(style = cell_fill(color = "#c05e85"), locations = cells_body(rows = player_position == "QB")) %>%
    tab_style(style = cell_fill(color = "#46a2ca"), locations = cells_body(rows = player_position == "WR")) %>%
    tab_style(style = cell_fill(color = "#73c3a6"), locations = cells_body(rows = player_position == "TE")) %>%
    tab_style(style = cell_fill(color = "#cc8c4a"), locations = cells_body(rows = player_position == "RB"))}
```


```{r cars, echo=FALSE}
div(
  style = "display: flex; gap: 7px;",
  div(GetRosterGT("McCadeP8")),
  div(GetRosterGT("tksimpson14")),
  div(GetRosterGT("Sweezzy")),
  div(GetRosterGT("sterlingcole"))
)
div(
  style = "display: flex; gap: 7px;",
  div(GetRosterGT("perc3val")),
  div(GetRosterGT("ThongBonestorm")),
  div(GetRosterGT("TobesEA")),
  div(GetRosterGT("DickLongshaft"))
)
```

```{r, echo=FALSE}
div(
  style = "display: flex; gap: 7px;",
  div(GetRosterPosition("QB")),
  div(GetRosterPosition("RB")),
  div(GetRosterPosition("WR")),
  div(GetRosterPosition("TE"))
)
```

```{r, echo=FALSE}
Designations %>%
  left_join(SnapCounts, by = c('Player' = 'player')) %>%
  filter(Redshirted == "No") %>%
  mutate(GP = ifelse(is.na(GP) == T, 0, GP),
         Classification = factor(Classification, levels = c("Senior", "Junior", "Sophomore", "Freshman"))) %>%
  filter(GP <= 4) %>%
  arrange(-GP) %>%
  select(-Redshirted) %>%
  arrange(-GP, Classification, Player) %>%
  filter(Player != "Kenneth Walker") %>%
  filter(Player != "Tyrone Tracy") %>%
  filter(Player != "Oronde Gadsden") %>%
  filter(Player != "Tre' Harris") %>%
gt() %>%
    gt_theme_espn() %>%
    cols_align(columns = everything(), align = 'center') %>%
    cols_align(columns = Player, align = 'left') %>%
    tab_header(title = md("Redshirts"))
```

