---
title: "Area Accurate Venn Diagram"
author: "McCade Pearson"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

<style>
@import url('https://fonts.googleapis.com/css2?family=Barlow+Semi+Condensed:wght@300;400;600;700&display=swap');

body {
  background-color: #0D1117;
  color: #F0F3F5;
  font-family: 'Barlow Semi Condensed', sans-serif;
  font-size: 16px;
  line-height: 1.6;
  margin: 0;
  padding: 20px;
}

.main-container {
  max-width: 1000px;
  margin: 0 auto;
  background-color: #1C1F26;
  padding: 40px;
  border: 2px solid #3E92CC;
  border-radius: 8px;
}

h1, h2, h3, h4, h5, h6 {
  color: #C3DDFD;
  font-weight: 600;
  margin-top: 30px;
  margin-bottom: 15px;
}

h1 {
  font-size: 2.2em;
  text-align: center;
  border-bottom: 3px solid #3E92CC;
  padding-bottom: 10px;
}

h2 {
  font-size: 1.8em;
  color: #6FB1FC;
}

h3 {
  font-size: 1.4em;
  color: #326DA8;
}

pre {
  background-color: #0D1117;
  border: 1px solid #3E92CC;
  border-radius: 5px;
  padding: 15px;
  overflow-x: auto;
}

code {
  background-color: #1C1F26;
  color: #C3DDFD;
  padding: 2px 4px;
  border-radius: 3px;
  font-family: 'Courier New', monospace;
}

pre code {
  background-color: transparent;
  padding: 0;
}

a {
  color: #6FB1FC;
  text-decoration: none;
}

a:hover {
  color: #C3DDFD;
  text-decoration: underline;
}

blockquote {
  border-left: 4px solid #3E92CC;
  margin: 20px 0;
  padding-left: 20px;
  color: #C3DDFD;
  font-style: italic;
}

table {
  border-collapse: collapse;
  width: 100%;
  margin: 20px 0;
}

th, td {
  border: 1px solid #3E92CC;
  padding: 12px;
  text-align: left;
}

th {
  background-color: #326DA8;
  color: #F0F3F5;
  font-weight: 600;
}

tr:nth-child(even) {
  background-color: #1C1F26;
}

.author, .date {
  text-align: center;
  color: #6FB1FC;
  font-size: 1.1em;
}

.insight-box {
  background-color: #1D3557;
  border-left: 4px solid #6FB1FC;
  padding: 15px;
  margin: 20px 0;
  border-radius: 5px;
}
</style>

## The Problem with Traditional Venn Diagrams

Most Venn diagrams lie to you. They show categorical relationships but completely ignore the actual magnitude of those relationships. When analyzing player combinations, team performance, or any quantitative overlap, traditional Venn diagrams can be misleading—making small overlaps appear massive and large overlaps seem insignificant.

**This project solves that problem by creating area-accurate Venn diagrams where circle sizes and overlap areas are mathematically proportional to the actual data values.**

## Why Area Accuracy Matters in Analytics

In sports analytics—and business analytics more broadly—proportional representation is crucial for decision-making. Consider these scenarios:

- **Roster Construction**: Understanding the true impact of player combinations
- **Resource Allocation**: Visualizing where investments overlap and where gaps exist  
- **Performance Analysis**: Seeing the actual magnitude of synergistic effects

Traditional visualizations can mislead stakeholders about these relationships. Area-accurate diagrams provide immediate, intuitive understanding of both individual contributions and collaborative effects.

## Technical Implementation

The mathematical challenge lies in determining the optimal distance between two circles to achieve a specific overlap area. This requires solving circle-circle intersection equations iteratively.

```{r setup, include=FALSE}
library(tidyverse)
library(ggtext)
library(ggforce)
library(showtext)
library(sysfonts)
library(zoo)
```

### Custom Theme Development

Building professional visualizations requires consistent branding and optimal readability. The McCadeP8 theme system ensures every chart maintains visual coherence while highlighting key insights.

```{r Theme, warning = FALSE, message = FALSE, include = FALSE}
McCadeP8_theme_colors <- c(
  background = '#0D1117',   # dark slate gray (background)
  text       = '#F0F3F5',   # very light gray (text)
  panel      = '#1C1F26',   # near-black with blue hint (panel)
  border     = '#3E92CC',   # strong blue (border)
  strip_text = '#0D1117',   # matches background (strip text on light facet)
  lighter    = '#C3DDFD',   # baby blue
  light      = '#6FB1FC',   # sky blue
  medium     = '#326DA8',   # Jazz navy
  dark       = '#1D3557'    # deep indigo/navy
)

McCadeP8_palette <- c(
  '#C3DDFD', '#F94144', '#6A4C93', '#F9C74F', '#43AA8B',
  '#577590', '#F3722C', '#277DA1', '#264653'
)

## McCade Pearson
## theme_McCadeP8
## Date Created: June 10, 2025

# THEME COLOR PALETTE --------------------------------------

#' McCadeP8 Inspired Theme Color Palette
#'
#' @format character vector of hex code strings
#' @export
#' @concept McCadeP8
#'
McCadeP8_theme_colors <- c(
  background = '#0D1117',
  text       = '#F0F3F5',
  panel      = '#1C1F26',
  border     = '#3E92CC',
  strip_text = '#0D1117',
  lighter    = '#C3DDFD',
  light      = '#6FB1FC',
  medium     = '#326DA8',
  dark       = '#1D3557'
)

# DISCRETE COLOR PALETTE -----------------------------------

#' McCadeP8 Inspired Color Palette
#'
#' @format character vector of hex code strings
#' @export
#' @concept McCadeP8
#'
McCadeP8_palette <- c(
  '#C3DDFD', '#F94144', '#6A4C93', '#F9C74F', '#43AA8B',
  '#577590', '#F3722C', '#277DA1', '#264653'
)

# MAIN THEME ------------------------------------------------

#' McCadeP8 Inspired Theme
#'
#' @param McCadeP8_font should `theme_McCadeP8` use custom font? Default is `TRUE`.
#' @param ... additional parameters to pass to `ggplot2::theme()`
#'
#' @return a `ggplot2` `theme` object
#' @export
#' @concept McCadeP8
#'
theme_McCadeP8 <- function(McCadeP8_font = TRUE, ...) {

  # Load custom Google Font
  font_family <- ifelse(McCadeP8_font, "Barlow Semi Condensed", "sans")
  if (McCadeP8_font) {
  font_add_google(name = "Barlow Semi Condensed", family = "Barlow Semi Condensed")
  showtext_auto()
  }

  # Define the theme
  ggplot2::theme(
    plot.background = element_rect(fill = McCadeP8_theme_colors["background"], color = NA),
    panel.background = element_rect(fill = McCadeP8_theme_colors["panel"], color = NA),
    panel.border = element_rect(color = McCadeP8_theme_colors["border"], fill = NA, linewidth = 1.2),
    panel.grid.major = element_line(color = "#2D3748", size = 0.25),
    panel.grid.minor = element_blank(),
    
    text = element_text(color = McCadeP8_theme_colors["text"], family = font_family),
    title = element_text(size = 20, face = "bold", hjust = 0.5),
    axis.title = element_text(size = 17),
    axis.text = element_text(size = 13, color = McCadeP8_theme_colors["text"]),
    axis.ticks = element_line(color = McCadeP8_theme_colors["border"], linewidth = 1),
    
    legend.background = element_rect(fill = McCadeP8_theme_colors["panel"], color = NA),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 14, face = "bold"),
    
    strip.background = element_rect(fill = McCadeP8_theme_colors["lighter"], colour = McCadeP8_theme_colors["border"]),
    strip.text = element_text(colour = McCadeP8_theme_colors["strip_text"], size = 10)
  )
}

# COLOR SCALES ---------------------------------------------

#' McCadeP8 Inspired Color Scales
#'
#' @param ... Additional arguments to pass to `ggplot2::binned_scale` for `_b`,
#' `ggplot2::scale_[fill/color]_gradient` for `_c`, or `ggplot2::discrete_scale`
#' for `_d`
#'
#' @rdname scale_McCadeP8
#' @export
scale_color_McCadeP8_c <- function(...) {
  ggplot2::scale_color_gradient(..., low = McCadeP8_theme_colors["light"], high = McCadeP8_theme_colors["dark"])
}

#' @rdname scale_McCadeP8
#' @export
scale_fill_McCadeP8_c <- function(...) {
  ggplot2::scale_fill_gradient(..., low = McCadeP8_theme_colors["light"], high = McCadeP8_theme_colors["dark"])
}

#' @rdname scale_McCadeP8
#' @export
scale_color_McCadeP8_b <- function(...) {
  if (!requireNamespace('scales', quietly = TRUE)) {
    stop('This function requires the `scales` R package.')
  }
  ramp <- scales::colour_ramp(c(McCadeP8_theme_colors["light"], McCadeP8_theme_colors["dark"]))
  ggplot2::binned_scale('color', 'McCadeP8', palette = ramp, ...)
}

#' @rdname scale_McCadeP8
#' @export
scale_fill_McCadeP8_b <- function(...) {
  if (!requireNamespace('scales', quietly = TRUE)) {
    stop('This function requires the `scales` R package.')
  }
  ramp <- scales::colour_ramp(c(McCadeP8_theme_colors["light"], McCadeP8_theme_colors["dark"]))
  ggplot2::binned_scale('fill', 'McCadeP8', palette = ramp, ...)
}

#' @rdname scale_McCadeP8
#' @export
scale_color_McCadeP8_d <- function(...) {
  ggplot2::discrete_scale(aesthetics = 'color',
                          palette = rot_pal(McCadeP8_palette), ...)
}

#' @rdname scale_McCadeP8
#' @export
scale_fill_McCadeP8_d <- function(...) {
  ggplot2::discrete_scale(aesthetics = 'fill',
                          palette = rot_pal(McCadeP8_palette), ...)
}

# Aliases
#' @rdname scale_McCadeP8
#' @export
scale_colour_McCadeP8_d <- scale_color_McCadeP8_d
#' @rdname scale_McCadeP8
#' @export
scale_colour_McCadeP8_c <- scale_color_McCadeP8_c
#' @rdname scale_McCadeP8
#' @export
scale_colour_McCadeP8_b <- scale_color_McCadeP8_b
```

### Mathematical Foundation

The core challenge is calculating precise circle overlap areas and determining optimal positioning. These functions handle the geometric calculations required for area-accurate representation.

```{r Part2, warning = FALSE, message = FALSE, include = FALSE}
circleCircleIntersectionArea <- function(d, r, R) {
  d <- max(min(d, r + R), abs(r - R))
  return(r^2 * acos((d^2 + r^2 - R^2) / (2 * d * r)) +
           R^2 * acos((d^2 + R^2 - r^2) / (2 * d * R)) -
           0.5 * sqrt((-d + r + R) * (d + r - R) * (d - r + R) * (d + r + R)))
}
findDistance <- function(r, R, A, eta = 0.0001) {
  if (A > r^2 * pi || A > R^2 * pi) {
    return(abs(r - R))}
  
  if (A < eta) {
    return(r + R)}
  
  gd <- function(minD = abs(r - R), maxD = r + R) {
    d <- (maxD + minD) / 2
    guess <- circleCircleIntersectionArea(d, r, R) # Note: circleCircleIntersectionArea is not defined in R
    if (abs(guess - A) < eta) {
      return(d)}
    
    # too much overlap, need more separation
    if (guess > A) {
      return(gd(d, maxD))}
    
    # otherwise, too little overlap, need less separation
    return(gd(minD, d))}
  return(gd())}
```

---

## Analysis 1: Utah Hockey Club's Dynamic Duo

The Utah Hockey Club's emergence as a competitive franchise depends heavily on key player combinations. By analyzing goal involvement data, we can identify which partnerships drive offensive success.

<div class="insight-box">
**Key Insight**: This visualization reveals that Keller and Schmaltz have significant individual impact (63 and 90 goals respectively) with meaningful collaborative contribution (42 goals together). The proportional representation shows Keller's efficiency as a primary scorer while highlighting Schmaltz's emerging role as a complementary playmaker.
</div>

```{r Part3, warning = FALSE, message = FALSE}
UHC_GoalScorers <- read.csv("UHC_GoalScorers.csv")

TopPair <- UHC_GoalScorers %>%
  mutate(Goal = row_number()) %>%
  rowwise() %>%
  mutate(pair_list = list(combn(na.omit(c(Scorer, Assist1, Assist2)), 2, simplify = FALSE))) %>%
  unnest(pair_list) %>%
  mutate(pair = map_chr(pair_list, ~ paste(sort(.x), collapse = " & "))) %>%
  ungroup() %>%
  count(pair, sort = TRUE) %>%
  head(1)

AB <- 42
A <- 63
B <- 90
nAB <- 240
A2 <- A-AB
B2 <- B-AB
ARadius <- sqrt(A/pi)
BRadius <- sqrt(B/pi)
nAB1 <- nAB/1.616
nAB1 <- sqrt(nAB1)
nAB2 <- nAB1*1.616

D <- findDistance(ARadius, BRadius, AB, eta = 0.0001)
D <- D/2

Point1 <- nAB2/2-D-BRadius
Point2 <- nAB2/2+D-ARadius
Point3 <- nAB2/2-D+BRadius
Point4 <- nAB2/2+D+ARadius
L1 <- (Point1+Point2)/2
L2 <- (Point3+Point4)/2
Z <- (Point2+Point3)/2

ggplot() +
  geom_rect(aes(xmin = 0, xmax = nAB2, ymin = 0, ymax = nAB1), color = "white", fill = "#1C1F26", alpha = 0.7, size = 1) +
  geom_label(aes(x = nAB2*0.90, y = nAB1*0.90, label = nAB-A-B+AB), size = 10) +
  geom_circle(aes(x0 = nAB2/2-D, y0 = nAB1/2, r = BRadius), color = "white", fill = "#6FB1FC", size = 1, alpha = 0.6) +
  geom_circle(aes(x0 = nAB2/2+D, y0 = nAB1/2, r = ARadius), color = "white", fill = "#1D3557", size = 1, alpha = 0.6) +
  geom_label(aes(x = L1, y = nAB1/2, label = B2), size = 10) +
  geom_label(aes(x = L2, y = nAB1/2, label = A2), size = 10) +
  geom_label(aes(x = Z, y = nAB1/2, label = AB), size = 10) +
  geom_label(aes(x = nAB2*0.90, y = nAB1*0.10, label = paste("Total:",nAB)), size = 10) +
  theme(aspect.ratio = 0.616) +
  theme_McCadeP8() +
  theme(aspect.ratio = 0.616,
        panel.background = element_rect(fill = "black"),
        plot.background = element_rect(fill = "black"),
        panel.grid = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        axis.title = element_blank(),
        panel.border = element_blank(),
        legend.position = "none",
        plot.subtitle = element_text(face = "bold", size = 20, hjust = 0.5),
        plot.title = element_markdown(face = "bold", size = 36, hjust = 0.5),
        plot.caption = element_text(size = 36)) +
labs(title = "Dynamic Duo: <span style='color:#6FB1FC'>Keller</span> & <span style='color:#1D3557'>Schmaltz's</span> Impact on the Scoreboard",
     subtitle = "A Proportional Venn Diagram of Their Goal Involvement — Together and Apart — During the 2024–25 Season",
     caption = "@McCadeP8 | Data: hockey-reference")
```

**Business Impact**: This analysis helps coaching staff understand optimal line combinations and can inform contract negotiations by quantifying collaborative value versus individual contribution.

---

## Analysis 2: Utah Jazz Frontcourt Analytics

NBA success increasingly depends on two-man game effectiveness. By analyzing net rating data for Walker Kessler and Lauri Markkanen, we can assess their synergistic impact on team performance.

<div class="insight-box">
**Key Insight**: The negative net ratings across all scenarios reveal systemic team challenges beyond individual player performance. However, the proportional analysis shows that Kessler-Markkanen combinations perform relatively better (-8.84 per 48 minutes) compared to other lineups, suggesting they should remain a focal point despite broader team struggles.
</div>

```{r Part4, warning = FALSE, message = FALSE}
AB <- 962
A <- 1476
B <- 1740
nAB <- 3961
A2 <- A-AB
B2 <- B-AB
ARadius <- sqrt(A/pi)
BRadius <- sqrt(B/pi)
nAB1 <- nAB/1.616
nAB1 <- sqrt(nAB1)
nAB2 <- nAB1*1.616

D <- findDistance(ARadius, BRadius, AB, eta = 0.0001)
D <- D/2

Point1 <- nAB2/2-D-BRadius
Point2 <- nAB2/2+D-ARadius
Point3 <- nAB2/2-D+BRadius
Point4 <- nAB2/2+D+ARadius
L1 <- (Point1+Point2)/2
L2 <- (Point3+Point4)/2
Z <- (Point2+Point3)/2

ggplot() +
  geom_rect(aes(xmin = 0, xmax = nAB2, ymin = 0, ymax = nAB1), color = "white", fill = "#1C1F26", alpha = 0.7, size = 1) +
  geom_label(aes(x = nAB2*0.90, y = nAB1*0.90, label = round((-429/(nAB-A-B+AB)*48),2)), size = 10) +
  geom_circle(aes(x0 = nAB2/2-D, y0 = nAB1/2, r = BRadius), color = "white", fill = "#6FB1FC", size = 1, alpha = 0.6) +
  geom_circle(aes(x0 = nAB2/2+D, y0 = nAB1/2, r = ARadius), color = "white", fill = "#1D3557", size = 1, alpha = 0.6) +
  geom_label(aes(x = L1, y = nAB1/2, label = round((-151/B2*48),2)), size = 10) +
  geom_label(aes(x = L2, y = nAB1/2, label = round((-8/A2*48),2)), size = 10) +
  geom_label(aes(x = Z, y = nAB1/2, label = round((-178/AB*48),2)), size = 10) +
  geom_label(aes(x = nAB2*0.90, y = nAB1*0.10, label = paste("Total:",-9.28)), size = 10) +
  theme(aspect.ratio = 0.616) +
  theme_McCadeP8() +
  theme(aspect.ratio = 0.616,
        panel.background = element_rect(fill = "black"),
        plot.background = element_rect(fill = "black"),
        panel.grid = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        axis.title = element_blank(),
        panel.border = element_blank(),
        legend.position = "none",
        plot.subtitle = element_text(face = "bold", size = 20, hjust = 0.5),
        plot.title = element_markdown(face = "bold", size = 36, hjust = 0.5),
        plot.caption = element_text(size = 36)) +
labs(  title = "<span style='color:#6FB1FC'>Walker Kessler</span> & <span style='color:#1D3557'>Lauri Markkanen</span>: Two-Man Synergy",
  subtitle = "Circle size = Minutes Played • Label = Net Points per 48 Minutes",
  caption = "@McCadeP8 | Data: basketball-reference")
```

**Strategic Implications**: The data suggests building around the Kessler-Markkanen core while addressing peripheral roster construction issues. Their sizeable overlap (962 minutes) provides substantial sample size for confidence in the analysis.

---

## Analysis 3: Golf's Greatest Rivalry

Tiger Woods versus Phil Mickelson represents one of sports' most compelling rivalries. By examining their major championship top-10 finishes from 1996-2015, we can quantify their competitive balance during golf's modern era.

<div class="insight-box">
**Key Insight**: Despite Tiger's reputation for dominance, this proportional analysis reveals a more balanced rivalry than commonly perceived. Tiger's 33 top-10 finishes versus Phil's 37 shows remarkable competitive parity, with 15 majors where both players finished in the top 10 simultaneously—creating golf's most compelling head-to-head drama.
</div>

```{r Part5, warning = FALSE, message = FALSE}
AB <- 15
A <- 33
B <- 37
nAB <- 80
A2 <- A-AB
B2 <- B-AB
ARadius <- sqrt(A/pi)
BRadius <- sqrt(B/pi)
nAB1 <- nAB/1.616
nAB1 <- sqrt(nAB1)
nAB2 <- nAB1*1.616

D <- findDistance(ARadius, BRadius, AB, eta = 0.0001)
D <- D/2

Point1 <- nAB2/2-D-BRadius
Point2 <- nAB2/2+D-ARadius
Point3 <- nAB2/2-D+BRadius
Point4 <- nAB2/2+D+ARadius
L1 <- (Point1+Point2)/2
L2 <- (Point3+Point4)/2
Z <- (Point2+Point3)/2

ggplot() +
  geom_rect(aes(xmin = 0, xmax = nAB2, ymin = 0, ymax = nAB1), color = "white", fill = "#1C1F26", alpha = 0.7, size = 1) +
  geom_label(aes(x = nAB2*0.90, y = nAB1*0.90, label = nAB-A-B+AB), size = 10) +
  geom_circle(aes(x0 = nAB2/2-D, y0 = nAB1/2, r = BRadius), color = "white", fill = "#6FB1FC", size = 1, alpha = 0.6) +
  geom_circle(aes(x0 = nAB2/2+D, y0 = nAB1/2, r = ARadius), color = "white", fill = "#1D3557", size = 1, alpha = 0.6) +
  geom_label(aes(x = L1, y = nAB1/2, label = B2), size = 10) +
  geom_label(aes(x = L2, y = nAB1/2, label = A2), size = 10) +
  geom_label(aes(x = Z, y = nAB1/2, label = AB), size = 10) +
  geom_label(aes(x = nAB2*0.90, y = nAB1*0.10, label = paste("Total:",nAB)), size = 10) +
  theme(aspect.ratio = 0.616) +
  theme_McCadeP8() +
  theme(aspect.ratio = 0.616,
        panel.background = element_rect(fill = "black"),
        plot.background = element_rect(fill = "black"),
        panel.grid = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        axis.title = element_blank(),
        panel.border = element_blank(),
        legend.position = "none",
        plot.subtitle = element_text(face = "bold", size = 20, hjust = 0.5),
        plot.title = element_markdown(face = "bold", size = 36, hjust = 0.5),
        plot.caption = element_text(size = 36)) +
labs(title = "<span style='color:#6FB1FC'>Tiger Woods</span> & <span style='color:#1D3557'>Phil Mickelson's</span> Generational Battle",
     subtitle = "Top-10 Finishes in Majors (1996–2015)",
     caption = "@McCadeP8 | Data: Wikipedia")
```

**Historical Context**: This analysis reframes our understanding of golf's modern era, showing that sustained excellence over two decades created one of sport's most compelling competitive narratives—where both players pushed each other to greatness.

---

## Key Takeaways & Business Applications

**Methodological Innovation**: Area-accurate Venn diagrams provide superior insight for any scenario involving overlapping quantitative relationships—from marketing campaign reach analysis to operational efficiency assessments.

**Analytical Precision**: Traditional visualizations can mislead decision-makers about the relative importance of individual versus collaborative contributions. This approach eliminates that ambiguity.

**Scalable Framework**: The mathematical foundation and custom visualization system can be adapted for diverse analytical challenges across industries, from sports performance to business intelligence.

**Storytelling Impact**: By combining rigorous mathematical accuracy with compelling visual narratives, complex analytical insights become immediately accessible to both technical and executive audiences.

This project demonstrates end-to-end analytical capability: identifying a visualization problem, developing a mathematical solution, implementing custom code, and delivering actionable insights through engaging storytelling.