---
title: "McCade Sports Recap"
author: "McCade Pearson"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

<style>
@import url('https://fonts.googleapis.com/css2?family=Barlow+Semi+Condensed:wght@300;400;600;700&display=swap');

body {
  background-color: #0D1117;
  color: #F0F3F5;
  font-family: 'Barlow Semi Condensed', sans-serif;
  font-size: 16px;
  line-height: 1.6;
  margin: 0;
  padding: 20px;
}

.main-container {
  max-width: 1000px;
  margin: 0 auto;
  background-color: #1C1F26;
  padding: 40px;
  border: 2px solid #3E92CC;
  border-radius: 8px;
}

h1, h2, h3, h4, h5, h6 {
  color: #C3DDFD;
  font-weight: 600;
  margin-top: 30px;
  margin-bottom: 15px;
}

h1 {
  font-size: 2.2em;
  text-align: center;
  border-bottom: 3px solid #3E92CC;
  padding-bottom: 10px;
}

h2 {
  font-size: 1.8em;
  color: #6FB1FC;
}

h3 {
  font-size: 1.4em;
  color: #326DA8;
}

pre {
  background-color: #0D1117;
  border: 1px solid #3E92CC;
  border-radius: 5px;
  padding: 15px;
  overflow-x: auto;
}

code {
  background-color: #1C1F26;
  color: #C3DDFD;
  padding: 2px 4px;
  border-radius: 3px;
  font-family: 'Courier New', monospace;
}

pre code {
  background-color: transparent;
  padding: 0;
}

a {
  color: #6FB1FC;
  text-decoration: none;
}

a:hover {
  color: #C3DDFD;
  text-decoration: underline;
}

blockquote {
  border-left: 4px solid #3E92CC;
  margin: 20px 0;
  padding-left: 20px;
  color: #C3DDFD;
  font-style: italic;
}

table {
  border-collapse: collapse;
  width: 100%;
  margin: 20px 0;
}

th, td {
  border: 1px solid #3E92CC;
  padding: 12px;
  text-align: left;
}

th {
  background-color: #326DA8;
  color: #F0F3F5;
  font-weight: 600;
}

tr:nth-child(even) {
  background-color: #1C1F26;
}

.author, .date {
  text-align: center;
  color: #6FB1FC;
  font-size: 1.1em;
}

.insight-box {
  background-color: #1D3557;
  border-left: 4px solid #6FB1FC;
  padding: 15px;
  margin: 20px 0;
  border-radius: 5px;
}
</style>

```{r Theme, warning = FALSE, message = FALSE, include = FALSE}
library(tidyverse)
library(ggtext)
library(ggforce)
library(showtext)
library(sysfonts)
library(zoo)
library(hoopR)
library(data.table)
library(lubridate)
library(glue)
library(ggimage)



McCadeP8_theme_colors <- c(
  background = '#0D1117',   # dark slate gray (background)
  text       = '#F0F3F5',   # very light gray (text)
  panel      = '#1C1F26',   # near-black with blue hint (panel)
  border     = '#3E92CC',   # strong blue (border)
  strip_text = '#0D1117',   # matches background (strip text on light facet)
  lighter    = '#C3DDFD',   # baby blue
  light      = '#6FB1FC',   # sky blue
  medium     = '#326DA8',   # Jazz navy
  dark       = '#1D3557'    # deep indigo/navy
)

McCadeP8_palette <- c(
  '#C3DDFD', '#F94144', '#6A4C93', '#F9C74F', '#43AA8B',
  '#577590', '#F3722C', '#277DA1', '#264653'
)

## McCade Pearson
## theme_McCadeP8
## Date Created: June 10, 2025

# THEME COLOR PALETTE --------------------------------------

#' McCadeP8 Inspired Theme Color Palette
#'
#' @format character vector of hex code strings
#' @export
#' @concept McCadeP8
#'
McCadeP8_theme_colors <- c(
  background = '#0D1117',
  text       = '#F0F3F5',
  panel      = '#1C1F26',
  border     = '#3E92CC',
  strip_text = '#0D1117',
  lighter    = '#C3DDFD',
  light      = '#6FB1FC',
  medium     = '#326DA8',
  dark       = '#1D3557'
)

# DISCRETE COLOR PALETTE -----------------------------------

#' McCadeP8 Inspired Color Palette
#'
#' @format character vector of hex code strings
#' @export
#' @concept McCadeP8
#'
McCadeP8_palette <- c(
  '#C3DDFD', '#F94144', '#6A4C93', '#F9C74F', '#43AA8B',
  '#577590', '#F3722C', '#277DA1', '#264653'
)

# MAIN THEME ------------------------------------------------

#' McCadeP8 Inspired Theme
#'
#' @param McCadeP8_font should `theme_McCadeP8` use custom font? Default is `TRUE`.
#' @param ... additional parameters to pass to `ggplot2::theme()`
#'
#' @return a `ggplot2` `theme` object
#' @export
#' @concept McCadeP8
#'
theme_McCadeP8 <- function(McCadeP8_font = TRUE, ...) {

  # Load custom Google Font
  font_family <- ifelse(McCadeP8_font, "Barlow Semi Condensed", "sans")
  if (McCadeP8_font) {
  font_add_google(name = "Barlow Semi Condensed", family = "Barlow Semi Condensed")
  showtext_auto()
  }

  # Define the theme
  ggplot2::theme(
    plot.background = element_rect(fill = McCadeP8_theme_colors["background"], color = NA),
    panel.background = element_rect(fill = McCadeP8_theme_colors["panel"], color = NA),
    panel.border = element_rect(color = McCadeP8_theme_colors["border"], fill = NA, linewidth = 1.2),
    panel.grid.major = element_line(color = "#2D3748", size = 0.25),
    panel.grid.minor = element_blank(),
    
    text = element_text(color = McCadeP8_theme_colors["text"], family = font_family),
    title = element_text(size = 20, face = "bold", hjust = 0.5),
    axis.title = element_text(size = 17),
    axis.text = element_text(size = 13, color = McCadeP8_theme_colors["text"]),
    axis.ticks = element_line(color = McCadeP8_theme_colors["border"], linewidth = 1),
    
    legend.background = element_rect(fill = McCadeP8_theme_colors["panel"], color = NA),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 14, face = "bold"),
    
    strip.background = element_rect(fill = McCadeP8_theme_colors["lighter"], colour = McCadeP8_theme_colors["border"]),
    strip.text = element_text(colour = McCadeP8_theme_colors["strip_text"], size = 10)
  )
}

# COLOR SCALES ---------------------------------------------

#' McCadeP8 Inspired Color Scales
#'
#' @param ... Additional arguments to pass to `ggplot2::binned_scale` for `_b`,
#' `ggplot2::scale_[fill/color]_gradient` for `_c`, or `ggplot2::discrete_scale`
#' for `_d`
#'
#' @rdname scale_McCadeP8
#' @export
scale_color_McCadeP8_c <- function(...) {
  ggplot2::scale_color_gradient(..., low = McCadeP8_theme_colors["light"], high = McCadeP8_theme_colors["dark"])
}

#' @rdname scale_McCadeP8
#' @export
scale_fill_McCadeP8_c <- function(...) {
  ggplot2::scale_fill_gradient(..., low = McCadeP8_theme_colors["light"], high = McCadeP8_theme_colors["dark"])
}

#' @rdname scale_McCadeP8
#' @export
scale_color_McCadeP8_b <- function(...) {
  if (!requireNamespace('scales', quietly = TRUE)) {
    stop('This function requires the `scales` R package.')
  }
  ramp <- scales::colour_ramp(c(McCadeP8_theme_colors["light"], McCadeP8_theme_colors["dark"]))
  ggplot2::binned_scale('color', 'McCadeP8', palette = ramp, ...)
}

#' @rdname scale_McCadeP8
#' @export
scale_fill_McCadeP8_b <- function(...) {
  if (!requireNamespace('scales', quietly = TRUE)) {
    stop('This function requires the `scales` R package.')
  }
  ramp <- scales::colour_ramp(c(McCadeP8_theme_colors["light"], McCadeP8_theme_colors["dark"]))
  ggplot2::binned_scale('fill', 'McCadeP8', palette = ramp, ...)
}

#' @rdname scale_McCadeP8
#' @export
scale_color_McCadeP8_d <- function(...) {
  ggplot2::discrete_scale(aesthetics = 'color',
                          palette = rot_pal(McCadeP8_palette), ...)
}

#' @rdname scale_McCadeP8
#' @export
scale_fill_McCadeP8_d <- function(...) {
  ggplot2::discrete_scale(aesthetics = 'fill',
                          palette = rot_pal(McCadeP8_palette), ...)
}

# Aliases
#' @rdname scale_McCadeP8
#' @export
scale_colour_McCadeP8_d <- scale_color_McCadeP8_d
#' @rdname scale_McCadeP8
#' @export
scale_colour_McCadeP8_c <- scale_color_McCadeP8_c
#' @rdname scale_McCadeP8
#' @export
scale_colour_McCadeP8_b <- scale_color_McCadeP8_b
```

# Packers

```{r}

dates <- format(seq(as.Date("2025-11-03"), as.Date("2026-04-06"), by = "day"), "%Y%m%d")
AllGamesList <- list()
for (i in seq_along(dates)) {
  DayGames <- espn_mbb_scoreboard(dates[i])
  AllGamesList[[i]] <- DayGames
  print(i)
}

AllGames <- rbindlist(AllGamesList, fill = TRUE)

GetSchedule <- function(Team_Abb) {
FilteredGames <- AllGames %>%
  filter(away_team_abb == Team_Abb | home_team_abb == Team_Abb)}
```

```{r}
BYUGames <- GetSchedule("BYU")

game_id <- 401827717

PBP <- hoopR::espn_mbb_pbp(game_id)
WP <- hoopR::espn_mbb_wp(game_id)

WPVisual <- function(game_id) {


  WP_Clean <- WP %>%
    select(home_win_percentage, play_id)
  PBP_Clean <- PBP %>%
    left_join(WP_Clean, by = c('play_id')) %>%
    select(text, home_win_percentage, shooting_play, scoring_play, away_score, home_score, home_team_abbrev, home_team_logo, home_team_full_name, home_team_color, away_team_logo,            away_team_abbrev, away_team_full_name, away_team_color, game_date_time, clock_display_value, period_number) %>%
    mutate(home_team_color = paste0("#",home_team_color),
           away_team_color = paste0("#",away_team_color),
           clock_sec = sapply(strsplit(clock_display_value, ":"), function(x) {as.numeric(x[1]) * 60 + as.numeric(x[2])}),
           seconds_remaining = case_when(
                                  period_number == 1 ~ clock_sec + 1200,
                                  period_number == 2 ~ clock_sec,
                                  TRUE ~ (period_number-2)*-300+clock_sec)) %>%
    group_by(seconds_remaining) %>%
    mutate(Type = n():1) %>%
    filter(Type == 1)
  
  away_team_color = ifelse(PBP_Clean$away_team_color[1] == "#NA", "#000000", PBP_Clean$away_team_color[1])
  home_team_color = ifelse(PBP_Clean$home_team_color[1] == "#NA", "#000000", PBP_Clean$home_team_color[1])

  
  ggplot() +
    geom_area(data = PBP_Clean, aes(x = seconds_remaining, y = 1), fill = away_team_color) +
    geom_area(data = PBP_Clean, aes(x = seconds_remaining, y = home_win_percentage), fill = home_team_color, color = "white") +
    theme_McCadeP8() +
    scale_x_reverse(breaks = seq(0, 2400, by = 300),
    labels = c("0:00", "5:00", "10:00", "15:00", "20:00", "5:00", "10:00", "15:00", "20:00")) +
    scale_y_continuous(
    breaks = c(0, 0.25, 0.5, 0.75, 1),
    labels = c("100%", "75%", "50%", "75%", "100%")) +
    expand_limits(x = c(0, 2400), y = c(0, 1)) +
    labs(title = paste(PBP_Clean$away_team_full_name[1], "@", PBP_Clean$home_team_full_name[1]), 
         subtitle = PBP_Clean$game_date_time[1], 
         caption = "@McCadeP8", 
         x = "", 
         y = "") +
    theme(panel.spacing = unit(0, "cm"), plot.margin = margin(0, 0, 0, 0), axis.ticks.length = unit(0.25, "cm"))}


GetStarters <- espn_mbb_player_box(401827693)
GetStarters <- GetStarters %>%
  filter(starter == TRUE) %>%
  select(athlete_display_name, team_short_display_name) %>%
  mutate(player = athlete_display_name,
         action = "in",
         team = team_short_display_name,
         seconds_remaining = 2400) %>%
  select(player, action, team, seconds_remaining)

PBP_Subs <- PBP %>%
  filter(grepl("subbing", text, ignore.case = TRUE)) %>%
  select(text, clock_display_value, period_number, away_score, home_score) %>%
  mutate(player = sub(" subbing .*", "", text), action = sub(".*subbing (in|out) .*", "\\1", text), team = sub(".*for (\\S+)$", "\\1", text)) %>%
  mutate(clock_sec = sapply(strsplit(clock_display_value, ":"), function(x) {as.numeric(x[1]) * 60 + as.numeric(x[2])}),
         seconds_remaining = case_when(
                                  period_number == 1 ~ clock_sec + 1200,
                                  period_number == 2 ~ clock_sec,
                                  TRUE ~ (period_number-2)*-300+clock_sec)) %>%
  select(player, action, team, seconds_remaining)

PBP_Subs <- rbind(GetStarters, PBP_Subs)

PBP_Subs <- PBP_Subs %>%
  group_by(action, player) %>%
  mutate(Shift = 1:n())

PBP_Subs2 <- PBP_Subs %>%
  select(player, action, team, seconds_remaining, Shift) %>%
  pivot_wider(
    names_from = action,  
    values_from = seconds_remaining, 
    values_fill = NA) %>%
  mutate(out = ifelse(is.na(out) == T, 0, out),
         in2 = `in`) %>%
  select(-`in`)

PBP_Scores <- PBP %>%
  mutate(clock_sec = sapply(strsplit(clock_display_value, ":"), function(x) {as.numeric(x[1]) * 60 + as.numeric(x[2])}),
         seconds_remaining = case_when(
                                  period_number == 1 ~ clock_sec + 1200,
                                  period_number == 2 ~ clock_sec,
                                  TRUE ~ (period_number-2)*-300+clock_sec)) %>%
  group_by(seconds_remaining) %>%
  mutate(Row = n():1) %>%
  filter(Row == 1) %>%
  select(home_score, away_score, seconds_remaining, home_team_color, away_team_color)

ht <- "BYU"


DataViz <- PBP_Subs2 %>%
  left_join(PBP_Scores, by = c('out' = 'seconds_remaining')) %>%
  left_join(PBP_Scores, by = c('in2' = 'seconds_remaining')) %>%
  mutate(home_team = ifelse(team == ht, T, F),
         points_scored = ifelse(home_team == T, home_score.x-home_score.y, away_score.x-away_score.y),
         points_allowed = ifelse(home_team == T, away_score.x-away_score.y, home_score.x-home_score.y),
         point_differential = points_scored-points_allowed,
         point_differential = ifelse(point_differential >= 0, paste0("+",point_differential), paste0(point_differential)),
         minutes_played2 = in2-out,
         minutes_played = minutes_played2/60,
         seconds_played = minutes_played-floor(minutes_played),
         seconds_played = seconds_played*60,
         seconds_played = sprintf("%02d", round(seconds_played)),
         minutes_played = floor(minutes_played),
         played = paste0(minutes_played, ":", seconds_played),
         team_color = ifelse(home_team == T, paste0("#",home_team_color.x), paste("#",away_team_color.x))) %>%
  select(player, team, out, in2, home_team_color.x, team_color, points_scored, points_allowed, point_differential, played, minutes_played2) %>%
  filter(team == ht) %>%
  arrange(in2) %>%
  group_by(player) %>%
  mutate(first_appearance = max(in2)) %>%
  ungroup() %>%
  mutate(player = factor(player, levels = unique(player[order(first_appearance)])))


DataViz2 <- DataViz %>%
  filter(minutes_played2 >= 60)

ggplot() +
  geom_tile(data = DataViz, aes(x = (in2+out)/2, y = player, width = out-in2, height = 0.9), color = "white", fill = DataViz$team_color[1]) +
  geom_text(data = DataViz2, aes(x = (in2+out)/2, y = player, label = paste0(points_scored,"-",points_allowed,"; ", point_differential, " in ",played)), color = "white") +
  scale_x_reverse(breaks = seq(0, 2400, by = 300), labels = c("0:00", "5:00", "10:00", "15:00", "20:00", "5:00", "10:00", "15:00", "20:00")) +
  theme_McCadeP8() +
  labs(title = paste(PBP$away_team_full_name[1], "@", PBP$home_team_full_name[1]), 
       caption = "@McCadeP8", 
         x = "", 
         y = "")
```

```{r}
library(hockeyR)
A <- hockeyR::get_game_ids(2026)
B <- hockeyR::scrape_game(2025020018)
C <- hockeyR::calculate_toi(B)
```

```{r}
library(MLBScrapeR)
A <- MLBScrapeR::get_schedule(2025)
C <- MLBScrapeR::get_data_json(c(778563))
D <- MLBScrapeR::get_pbp_data(c(C))
```

```{r}
library(nflfastR)
A <- nflfastR::load_pbp(2025)
```

```{r}
library(cfbfastR)
A <- cfbfastR::espn_cfb_schedule(2025)
```
