---
title: "2025 SBCFBL Rule Changes"
author: "McCade Pearson"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

<style>
@import url('https://fonts.googleapis.com/css2?family=Barlow+Semi+Condensed:wght@300;400;600;700&display=swap');

body {
  background-color: #0D1117;
  color: #F0F3F5;
  font-family: 'Barlow Semi Condensed', sans-serif;
  font-size: 16px;
  line-height: 1.6;
  margin: 0;
  padding: 20px;
}

/* TOC Styling - Outside main container */
#TOC {
  background-color: #1C1F26 !important;
  border: 2px solid #3E92CC !important;
  border-radius: 8px !important;
  padding: 20px !important;
  margin-bottom: 20px !important;
  box-shadow: 0 4px 8px rgba(0, 0, 0, 0.3) !important;
}

#TOC ul {
  list-style-type: none !important;
  padding-left: 0 !important;
}

#TOC li {
  margin: 8px 0 !important;
}

#TOC a {
  color: #6FB1FC !important;
  text-decoration: none !important;
  font-weight: 400 !important;
  display: block !important;
  padding: 5px 10px !important;
  border-radius: 4px !important;
  transition: all 0.3s ease !important;
}

#TOC a:hover {
  background-color: #3E92CC !important;
  color: #F0F3F5 !important;
}

#TOC .tocify-header {
  color: #C3DDFD !important;
  font-weight: 600 !important;
  font-size: 1.1em !important;
  margin-bottom: 10px !important;
}

/* Floating TOC specific styles */
.tocify {
  background-color: #1C1F26 !important;
  border: 2px solid #3E92CC !important;
  border-radius: 8px !important;
}

.tocify-header {
  color: #C3DDFD !important;
}

.tocify-subheader {
  background-color: transparent !important;
}

.tocify-item {
  background-color: transparent !important;
}

.main-container {
  max-width: 1000px;
  margin: 0 auto;
  background-color: #1C1F26;
  padding: 40px;
  border: 2px solid #3E92CC;
  border-radius: 8px;
}

h1, h2, h3, h4, h5, h6 {
  color: #C3DDFD;
  font-weight: 600;
  margin-top: 30px;
  margin-bottom: 15px;
}

h1 {
  font-size: 2.2em;
  text-align: center;
  border-bottom: 3px solid #3E92CC;
  padding-bottom: 10px;
}

h2 {
  font-size: 1.8em;
  color: #6FB1FC;
}

h3 {
  font-size: 1.4em;
  color: #326DA8;
}

/* Fixed code block styling */
pre {
  background-color: #0D1117 !important;
  border: 1px solid #3E92CC !important;
  border-radius: 5px !important;
  padding: 15px !important;
  overflow-x: auto !important;
  color: #F0F3F5 !important;
}

code {
  background-color: #1C1F26 !important;
  color: #C3DDFD !important;
  padding: 2px 4px !important;
  border-radius: 3px !important;
  font-family: 'Courier New', monospace !important;
}

pre code {
  background-color: transparent !important;
  padding: 0 !important;
  color: #F0F3F5 !important;
}

/* Python syntax highlighting */
.sourceCode {
  background-color: #0D1117 !important;
  color: #F0F3F5 !important;
}

.sourceCode .kw { color: #ff7b72; } /* keywords */
.sourceCode .dt { color: #79c0ff; } /* data types */
.sourceCode .dv { color: #a5d6ff; } /* decimal values */
.sourceCode .bn { color: #a5d6ff; } /* base n */
.sourceCode .fl { color: #a5d6ff; } /* floats */
.sourceCode .ch { color: #a5d6ff; } /* chars */
.sourceCode .st { color: #a5d6ff; } /* strings */
.sourceCode .co { color: #8b949e; } /* comments */
.sourceCode .ot { color: #d2a8ff; } /* other */
.sourceCode .al { color: #f85149; } /* alerts */
.sourceCode .fu { color: #d2a8ff; } /* functions */
.sourceCode .er { color: #f85149; } /* errors */

a {
  color: #6FB1FC;
  text-decoration: none;
}

a:hover {
  color: #C3DDFD;
  text-decoration: underline;
}

blockquote {
  border-left: 4px solid #3E92CC;
  margin: 20px 0;
  padding-left: 20px;
  color: #C3DDFD;
  font-style: italic;
}

table {
  border-collapse: collapse;
  width: 100%;
  margin: 20px 0;
}

th, td {
  border: 1px solid #3E92CC;
  padding: 12px;
  text-align: left;
}

th {
  background-color: #326DA8;
  color: #F0F3F5;
  font-weight: 600;
}

tr:nth-child(even) {
  background-color: #1C1F26;
}

.author, .date {
  text-align: center;
  color: #6FB1FC;
  font-size: 1.1em;
}

.insight-box {
  background-color: #1D3557;
  border-left: 4px solid #6FB1FC;
  padding: 15px;
  margin: 20px 0;
  border-radius: 5px;
}
</style>

```{r setup, include=FALSE}
library(tidyverse)
library(gt)
library(gtExtras)
library(googlesheets4)
library(showtext)
library(sysfonts)

gs4_deauth()
options(scipen = 99)
sheet_key <- "11YuW1DTPVid5OUcludvPE4-EqU751qp5l21lDK6V7PE"

SBC <- range_read(sheet_key, sheet = "SBCLogos")
RuleChanges2 <- read_csv("RuleChanges.csv")
RuleChanges <- RuleChanges2 %>%
  tail(nrow(.)-2) %>%
  mutate(StartDate = as.POSIXct(StartDate, tz = "UTC"),
         Q2 = ifelse(Q2 == 2, 0, 1),
         Q3 = ifelse(Q3 == 2, 0, 1),
         Q4 = ifelse(Q4 == 2, 0, 1),
         Q5 = ifelse(Q5 == 2, 0, 1),
         Team = case_when(Q1 == "TyF4LNkBNtAkEB4It2Hg" ~ "Albuquerque Armadillos",
                          Q1 == "FcLJLFN7i8QQiLYTzKWo" ~ "Anaheim Mice",
                          Q1 == "dGrUraAPmcqhK0m6ARWh" ~ "Anchorage Killer Whales",
                          Q1 == "ZSHHRH81oj8sMcEdoY1l" ~ "Austin Bats",
                          Q1 == "D1B6j2xcdgHQPMdF4QOq" ~ "Baltimore Blue Crabs",
                          Q1 == "bxVOCQ1S5Q8pPrEU57xc" ~ "Birmingham Bandits",
                          Q1 == "I6Pg736WoKYeVeI6U4e1" ~ "Boise Spuds",
                          Q1 == "5162yikwsApWCLrX4UJs" ~ "Buffalo Daredevils",
                          Q1 == "jMYWLR2XrzlL7I4rmUOU" ~ "Cincinnati Chili",
                          Q1 == "rdQy1hcby0rS88x8ZNFz" ~ "Columbus Arches",
                          Q1 == "foRQTbf7X7sPzwToUqAy" ~ "Des Moines Racoons",
                          Q1 == "MJ41zvbgwrKeZoTB7BWS" ~ "El Paso Vipers",
                          Q1 == "HMUEn4W03Foc41CAECZm" ~ "Honolulu Diamonds",
                          Q1 == "45voC1imU3u8KP5dUwsf" ~ "Jacksonville Manatees",
                          Q1 == "84F4QNW03LX2AI0s02dy" ~ "Kentucky Thoroughbreds",
                          Q1 == "cFUiAg0LIxSESHeKgN1B" ~ "Lansing Lagoon",
                          Q1 == "VoCm4cWh5PZm9VehkM4x" ~ "Lincoln Bully",
                          Q1 == "bEvPh9hsVSyir9NSr6tA" ~ "Little Rock Big Foot",
                          Q1 == "BzyHZbJO6jiPO80dACaC" ~ "Manchester Trout",
                          Q1 == "aU1nz37NW5o0JIHilRH7" ~ "Nashville Strings",
                          Q1 == "t5xL0w4jV8TpJwYGpjbx" ~ "Pittsburgh Bridge",
                          Q1 == "ZsszJyXaxCGg5E8vAb86" ~ "Providence Pilgrims",
                          Q1 == "ZsszJyXaxCGg5E8vAb96" ~ "Providence Pilgrims",
                          Q1 == "R0v8umk3ZaNp6OXaPYnB" ~ "San Diego Seals",
                          Q1 == "MQwfNLhUakQ13r7Ft1M4" ~ "San Jose Seagulls",
                          Q1 == "jsY6XYU5mzjSk7laetU3" ~ "Seattle Brew",
                          Q1 == "A8FpUrhgzTRMN1IOK4O9" ~ "St. Louis 66ers",
                          Q1 == "NPme2qXwpi0LBcY73EFF" ~ "Tampa Bay Flamingos",
                          Q1 == "iIwpWRN1I9fkcvki1y8N" ~ "Tulsa Tornado",
                          Q1 == "BMro1UdTd6X488MU7ket" ~ "Vancouver Forest",
                          Q1 == "M8n43ZSLcJGCfWeF0RFn" ~ "Vegas Blackjack")) %>%
  filter(is.na(Team) == F) %>%
  select(StartDate, Team, Q2, Q3, Q4, Q5) %>%
  group_by(Team) %>%
  mutate(Rk = rank(desc(StartDate))) %>%
  ungroup() %>%
  filter(Rk == 1) %>%
  select(-Rk)
```

```{r Theme, warning = FALSE, message = FALSE, include = FALSE, warning=FALSE, message=FALSE}
McCadeP8_theme_colors <- c(
  background = '#0D1117',   # dark slate gray (background)
  text       = '#F0F3F5',   # very light gray (text)
  panel      = '#1C1F26',   # near-black with blue hint (panel)
  border     = '#3E92CC',   # strong blue (border)
  strip_text = '#0D1117',   # matches background (strip text on light facet)
  lighter    = '#C3DDFD',   # baby blue
  light      = '#6FB1FC',   # sky blue
  medium     = '#326DA8',   # Jazz navy
  dark       = '#1D3557'    # deep indigo/navy
)

McCadeP8_palette <- c(
  '#C3DDFD', '#F94144', '#6A4C93', '#F9C74F', '#43AA8B',
  '#577590', '#F3722C', '#277DA1', '#264653'
)

## McCade Pearson
## theme_McCadeP8
## Date Created: June 10, 2025

# THEME COLOR PALETTE --------------------------------------

#' McCadeP8 Inspired Theme Color Palette
#'
#' @format character vector of hex code strings
#' @export
#' @concept McCadeP8
#'
McCadeP8_theme_colors <- c(
  background = '#0D1117',
  text       = '#F0F3F5',
  panel      = '#1C1F26',
  border     = '#3E92CC',
  strip_text = '#0D1117',
  lighter    = '#C3DDFD',
  light      = '#6FB1FC',
  medium     = '#326DA8',
  dark       = '#1D3557'
)

# DISCRETE COLOR PALETTE -----------------------------------

#' McCadeP8 Inspired Color Palette
#'
#' @format character vector of hex code strings
#' @export
#' @concept McCadeP8
#'
McCadeP8_palette <- c(
  '#C3DDFD', '#F94144', '#6A4C93', '#F9C74F', '#43AA8B',
  '#577590', '#F3722C', '#277DA1', '#264653'
)

# MAIN THEME ------------------------------------------------

#' McCadeP8 Inspired Theme
#'
#' @param McCadeP8_font should `theme_McCadeP8` use custom font? Default is `TRUE`.
#' @param ... additional parameters to pass to `ggplot2::theme()`
#'
#' @return a `ggplot2` `theme` object
#' @export
#' @concept McCadeP8
#'
theme_McCadeP8 <- function(McCadeP8_font = TRUE, ...) {

  # Load custom Google Font
  font_family <- ifelse(McCadeP8_font, "Barlow Semi Condensed", "sans")
  if (McCadeP8_font) {
  font_add_google(name = "Barlow Semi Condensed", family = "Barlow Semi Condensed")
  showtext_auto()
  }

  # Define the theme
  ggplot2::theme(
    plot.background = element_rect(fill = McCadeP8_theme_colors["background"], color = NA),
    panel.background = element_rect(fill = McCadeP8_theme_colors["panel"], color = NA),
    panel.border = element_rect(color = McCadeP8_theme_colors["border"], fill = NA, linewidth = 1.2),
    panel.grid.major = element_line(color = "#2D3748", size = 0.25),
    panel.grid.minor = element_blank(),
    
    text = element_text(color = McCadeP8_theme_colors["text"], family = font_family),
    title = element_text(size = 20, face = "bold", hjust = 0.5),
    axis.title = element_text(size = 17),
    axis.text = element_text(size = 13, color = McCadeP8_theme_colors["text"]),
    axis.ticks = element_line(color = McCadeP8_theme_colors["border"], linewidth = 1),
    
    legend.background = element_rect(fill = McCadeP8_theme_colors["panel"], color = NA),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 14, face = "bold"),
    
    strip.background = element_rect(fill = McCadeP8_theme_colors["lighter"], colour = McCadeP8_theme_colors["border"]),
    strip.text = element_text(colour = McCadeP8_theme_colors["strip_text"], size = 10)
  )
}

# COLOR SCALES ---------------------------------------------

#' McCadeP8 Inspired Color Scales
#'
#' @param ... Additional arguments to pass to `ggplot2::binned_scale` for `_b`,
#' `ggplot2::scale_[fill/color]_gradient` for `_c`, or `ggplot2::discrete_scale`
#' for `_d`
#'
#' @rdname scale_McCadeP8
#' @export
scale_color_McCadeP8_c <- function(...) {
  ggplot2::scale_color_gradient(..., low = McCadeP8_theme_colors["light"], high = McCadeP8_theme_colors["dark"])
}

#' @rdname scale_McCadeP8
#' @export
scale_fill_McCadeP8_c <- function(...) {
  ggplot2::scale_fill_gradient(..., low = McCadeP8_theme_colors["light"], high = McCadeP8_theme_colors["dark"])
}

#' @rdname scale_McCadeP8
#' @export
scale_color_McCadeP8_b <- function(...) {
  if (!requireNamespace('scales', quietly = TRUE)) {
    stop('This function requires the `scales` R package.')
  }
  ramp <- scales::colour_ramp(c(McCadeP8_theme_colors["light"], McCadeP8_theme_colors["dark"]))
  ggplot2::binned_scale('color', 'McCadeP8', palette = ramp, ...)
}

#' @rdname scale_McCadeP8
#' @export
scale_fill_McCadeP8_b <- function(...) {
  if (!requireNamespace('scales', quietly = TRUE)) {
    stop('This function requires the `scales` R package.')
  }
  ramp <- scales::colour_ramp(c(McCadeP8_theme_colors["light"], McCadeP8_theme_colors["dark"]))
  ggplot2::binned_scale('fill', 'McCadeP8', palette = ramp, ...)
}

#' @rdname scale_McCadeP8
#' @export
scale_color_McCadeP8_d <- function(...) {
  ggplot2::discrete_scale(aesthetics = 'color',
                          palette = rot_pal(McCadeP8_palette), ...)
}

#' @rdname scale_McCadeP8
#' @export
scale_fill_McCadeP8_d <- function(...) {
  ggplot2::discrete_scale(aesthetics = 'fill',
                          palette = rot_pal(McCadeP8_palette), ...)
}

# Aliases
#' @rdname scale_McCadeP8
#' @export
scale_colour_McCadeP8_d <- scale_color_McCadeP8_d
#' @rdname scale_McCadeP8
#' @export
scale_colour_McCadeP8_c <- scale_color_McCadeP8_c
#' @rdname scale_McCadeP8
#' @export
scale_colour_McCadeP8_b <- scale_color_McCadeP8_b
```

## Thank you for participating in the start of the 2025–26 SBCFBL Season. We’re excited to kick off our sixth great year!

#### One rule change was made at the sole discretion of the commissioner to improve the league: We will now play on a 1/3,000,000th scale instead of a 1/2,000,000th scale. This means everyone’s entry fees should be roughly 25% cheaper this year, accounting for the growing salary cap.

---

#### Do you vote to change the order in which players are signed in free agency from Alphabetical to a different system?   

Starting immediately, free agents signed on the same day will be signed in order of their Fantrax Fantasy ranking from the entire previous NBA regular season, rather than alphabetically as in the past.

```{r Plot0, fig.width=10, fig.height=4, warning=FALSE, message=FALSE, echo = FALSE}
Q2 <- RuleChanges %>%
  group_by(Q2) %>%
  summarize(Total = n()) %>%
  mutate(Vote = ifelse(Q2 == 1, "Yes", "No"),
         Vote = factor(Vote, levels = c("No", "Yes")),
         Group = "Change") 
Q2Q3 <- RuleChanges %>%
  group_by(Q2, Q3) %>%
  summarize(Total = n()) %>%
  ungroup() %>%
  mutate(Vote = case_when(
                  Q2 == 1 & Q3 == 1 ~ "Q2Yes_Q3Yes",
                  Q2 == 1 & Q3 == 0 ~ "Q2Yes_Q3No",
                  Q2 == 0 & Q3 == 1 ~ "Q2No_Q3Yes",
                  Q2 == 0 & Q3 == 0 ~ "Q2No_Q3No"),
         Vote = factor(Vote, levels = c("Q2No_Q3No", "Q2Yes_Q3No", "Q2No_Q3Yes", "Q2Yes_Q3Yes")), 
         Group = "PER") 
AllData <- bind_rows(Q2, Q2Q3)
AllData <- AllData %>%
  mutate(Group = factor(Group, levels = c("PER","Change")))

ggplot(AllData) +
  geom_col(aes(x = Group, y = Total, fill = Vote), position = "stack", width = 0.7) +
  geom_hline(yintercept = 19.5, color = "#B61A1C", linetype = "dashed", size = 1) +
  geom_hline(yintercept = 15.0, color = "#1A1CB6", linetype = "dashed", size = 1) +
  scale_fill_manual(values = c(
    "Yes" = "#309143",
    "No" = "#B61A1C",
    "Q2Yes_Q3Yes" = "#1E6028",
    "Q2Yes_Q3No" = "#66C26E",
    "Q2No_Q3Yes" = "#741113",
    "Q2No_Q3No" = "#E04A4C")) +
  coord_flip() +
  theme_McCadeP8() +
  scale_y_continuous(breaks = seq(2, 30, by = 2)) +
  theme(axis.text.y = element_text(size = 30), axis.text.x = element_text(size = 35), legend.position = "none") +
  labs(x = "", y = "", fill = "Response") 
```


---

#### Do you vote to change how the League Tax funds are used?

Tax funds will first be used to cover the Fantrax fee, then to cover the first $100 of the League Champion’s trophy. If the tax fund is insufficient to cover these expenses, the remaining balance will be taken from the prize pool. Any tax funds beyond those amounts will be split 50/50 between a charity chosen by the champion and the non–tax-paying teams.

```{r Plot1, fig.width=10, fig.height=2, warning=FALSE, message=FALSE, echo = FALSE}
RuleChanges %>%
  group_by(Q4) %>%
  summarize(Total = n()) %>%
  mutate(Vote = ifelse(Q4 == 1, "Yes", "No"), 
         Vote = factor(Vote, levels = c("No", "Yes"))) %>%
ggplot() +
  geom_col(aes(x = "", y = Total, fill = Vote), position = "stack", width = 1.0) +
  geom_hline(yintercept = 19.5, color = "#B61A1C", linetype = "dashed", size = 1) +
  scale_fill_manual(values = c("Yes" = "#309143", "No" = "#B61A1C")) +
  coord_flip() +
  theme_McCadeP8() +
  scale_y_continuous(breaks = seq(2, 30, by = 2)) +
  theme(axis.text.x = element_text(size = 30), legend.position = "none") +
  labs(x = "", y = "") 
```

---

#### Do you vote to change the current Fantrax roster setup?

Fantrax settings will be adjusted to reduce the bench from 14 roster spots to just six, effectively requiring a full starting lineup every day of the season. The total roster limit remains 17 players, with eight starters and three IR spots. Offseason rosters will still have 17 players but no IR spots.

```{r Plot2, fig.width=10, fig.height=2, warning=FALSE, message=FALSE, echo = FALSE}
RuleChanges %>%
  group_by(Q5) %>%
  summarize(Total = n()) %>%
  mutate(Vote = ifelse(Q5 == 1, "Yes", "No"), 
         Vote = factor(Vote, levels = c("No", "Yes"))) %>%
ggplot() +
  geom_col(aes(x = "", y = Total, fill = Vote), position = "stack", width = 1.0) +
  geom_hline(yintercept = 19.5, color = "#B61A1C", linetype = "dashed", size = 1) +
  scale_fill_manual(values = c("Yes" = "#309143", "No" = "#B61A1C")) +
  coord_flip() +
  theme_McCadeP8() +
  scale_y_continuous(breaks = seq(2, 30, by = 2)) +
  theme(axis.text.x = element_text(size = 30), legend.position = "none") +
  labs(x = "", y = "") 
```

---

#### All 30 teams have voted, and their votes are listed below.

```{r Plot3, warning=FALSE, message=FALSE, echo = FALSE}
RuleChanges %>%
  left_join(SBC, by = c('Team')) %>%
  arrange(Team) %>%
  select(Logo, Q2, Q3, Q4, Q5) %>%
  gt() %>%
  gt_theme_espn() %>%
  text_transform(locations = cells_body(columns = Logo),
              fn = function(x) {map_chr(x, function(path) {
              adjusted_path <- file.path("SBC_Cap_Sheets", path)
              if (file.exists(adjusted_path)) {local_image(filename = adjusted_path, height = 100)} 
              else {paste("Missing:", basename(path))}})}) %>%
  tab_header(title = "Individual Team Votes") %>%
  cols_align(columns = everything(), align = "center") %>%
  tab_style(style = list(cell_fill(color = "#B61A1C"), cell_text(color = "#B61A1C")),
            locations = cells_body(columns = Q2, rows = Q2 == 0)) %>%
  tab_style(style = list(cell_fill(color = "#B61A1C"), cell_text(color = "#B61A1C")),
            locations = cells_body(columns = Q3, rows = Q3 == 0)) %>%
  tab_style(style = list(cell_fill(color = "#B61A1C"), cell_text(color = "#B61A1C")),
            locations = cells_body(columns = Q4, rows = Q4 == 0)) %>%
  tab_style(style = list(cell_fill(color = "#B61A1C"), cell_text(color = "#B61A1C")),
            locations = cells_body(columns = Q5, rows = Q5 == 0)) %>%
  tab_style(style = list(cell_fill(color = "#309143"), cell_text(color = "#309143")),
            locations = cells_body(columns = Q2, rows = Q2 == 1)) %>%
  tab_style(style = list(cell_fill(color = "#309143"), cell_text(color = "#309143")),
            locations = cells_body(columns = Q3, rows = Q3 == 1)) %>%
  tab_style(style = list(cell_fill(color = "#309143"), cell_text(color = "#309143")),
            locations = cells_body(columns = Q4, rows = Q4 == 1)) %>%
  tab_style(style = list(cell_fill(color = "#309143"), cell_text(color = "#309143")),
            locations = cells_body(columns = Q5, rows = Q5 == 1)) %>%
  cols_label(Q2 = "Sign Order Change", 
             Q3 = "Player Efficiency Rating", 
             Q4 = "Tax Distribution Change", 
             Q5 = "Roster Limit Changes") %>%
  cols_width(c(Q2, Q3, Q4, Q5) ~ px(200)) %>%
  tab_options(heading.align = "center")
```

---

#### This shows how common each specific voting outcome was.

```{r Plot4, warning=FALSE, message=FALSE, echo = FALSE, fig.width= 10}
RuleChanges %>%
  group_by(Q2,Q3,Q4,Q5) %>%
  summarize(Total = n()) %>%
  ungroup() %>%
  arrange(-Total) %>%
  gt() %>%
  gt_theme_espn() %>%
  tab_header(title = "Most Common  Votes") %>%
  cols_align(columns = everything(), align = "center") %>%
  tab_style(style = list(cell_fill(color = "#B61A1C"), cell_text(color = "#B61A1C")),
            locations = cells_body(columns = Q2, rows = Q2 == 0)) %>%
  tab_style(style = list(cell_fill(color = "#B61A1C"), cell_text(color = "#B61A1C")),
            locations = cells_body(columns = Q3, rows = Q3 == 0)) %>%
  tab_style(style = list(cell_fill(color = "#B61A1C"), cell_text(color = "#B61A1C")),
            locations = cells_body(columns = Q4, rows = Q4 == 0)) %>%
  tab_style(style = list(cell_fill(color = "#B61A1C"), cell_text(color = "#B61A1C")),
            locations = cells_body(columns = Q5, rows = Q5 == 0)) %>%
  tab_style(style = list(cell_fill(color = "#309143"), cell_text(color = "#309143")),
            locations = cells_body(columns = Q2, rows = Q2 == 1)) %>%
  tab_style(style = list(cell_fill(color = "#309143"), cell_text(color = "#309143")),
            locations = cells_body(columns = Q3, rows = Q3 == 1)) %>%
  tab_style(style = list(cell_fill(color = "#309143"), cell_text(color = "#309143")),
            locations = cells_body(columns = Q4, rows = Q4 == 1)) %>%
  tab_style(style = list(cell_fill(color = "#309143"), cell_text(color = "#309143")),
            locations = cells_body(columns = Q5, rows = Q5 == 1)) %>%
  cols_label(Q2 = "Sign Order Change", 
             Q3 = "Player Efficiency Rating", 
             Q4 = "Tax Distribution Change", 
             Q5 = "Roster Limit Changes") %>%
  cols_width(c(Q2, Q3, Q4, Q5) ~ px(200)) %>%
  tab_options(heading.align = "center")
```

